### 2016-12-05 local-capability-machine.tex
Added create closure instruction

@@

>>>>

\item[\texttt{crtcls $[(x_1,r_1),\dots(x_n,r_n)]$ $r_{\var{code}}$}] \forcenewline
$[(x_1,r_1),\dots(x_n,r_n)]$ is a list of variable bindings. If an instruction refers to a variable, then it will assume that an environment is available in a designated register (say $r_{\var{env}}$). The register $r_{\var{code}}$ should contain a capability governs the code of the closure and that is executable when jumped to.
  \item[Allocate memory for variable environment]
  \item[Store register contents to environment]
  \item[Allocate memory for record with environment capability, code capability, and acitvation code]
  \item[Store capabilities and activation code to record]
  \item[Restrict the capability for the ``clojure pair'' to an enter capability]
  \item[Activation code:] \forcenewline
    \item Load the environment capability to a designated register
    \item Load the code capability.
    \item Jump to the code.
  A more detailed description of each step:
  \item[Allocate memory for variable environment] Have malloc allocate a piece of memory of size $n$ (the size of the variable environment). 
  \item[Store register contents to environment] Store the contents of each of the registers $r_1,\dots,r_n$ to the newly allocated memory
  \item[Allocate memory for record with environment capability, code capability, and acitvation code] Allocate a new piece of memory with room for a capability for the environment
  \item[Store capabilities and activation code to record] Store the environment capability and code capability in the record followed by the activation code. 
  \item[Restrict the capability for the ``clojure pair'' to an enter capability] Adjust the capability to point to the start of the acitvation code and restrict it to an enter capability.
  \item[Activation code:] \forcenewline
    \item Load the environment capability to a designated register.
    \item Load the code capability.
    \item Jump to the code.
\item[\texttt{load $r$ $x$}] Assumes environment capability available in register $r_{\var{env}}$. Loads the at the index associated with $x$ in the list. Loads from this capability into $r$.
\item[\texttt{store $x$ $r$}] Assumes environment capability available in register $r_{\var{env}}$. Loads the at the index associated with $x$ in the list. Stores the contents of register $r$ through this capability.

@@

\item The code of a closure will often be found in conjunction with the code that creates it.
